---
title: "README"
output:
  html_document:
    keep_md: yes
---


# rtext

A package with R6 object definitions for handling text and data


<br><br>**Description**

TBD



<br><br>**Status**

*unstable* - in wild developement with fuRiouS rEstRucturINg and biG biG pOKing

[![Travis-CI Build Status](https://travis-ci.org/petermeissner/rtext.svg?branch=master)](https://travis-ci.org/petermeissner/rtext)
[![codecov](https://codecov.io/gh/petermeissner/rtext/branch/master/graph/badge.svg)](https://codecov.io/gh/petermeissner/rtext/tree/master/R)
[![CRAN version](http://www.r-pkg.org/badges/version/stringb)](https://cran.r-project.org/package=rtext)


<br><br>**Citation**


```{r, results='asis', echo=FALSE}
citation("rtext")
```

<br><br>**BibTex for citing**

<code style="white-space:normal;">
```{r, results='asis', echo=FALSE}
toBibtex(citation("rtext"))
```
</code>



<br><br>**Installation**

```{r, eval=FALSE}
  devtools::install_github("petermeissner/stringb")    
  devtools::install_github("petermeissner/rtext")
  library(rtext)
```


    

<br><br>**Example Usage**

<br><br>*... starting up ...*

```{r}
library(stringb)
library(rtext)
options("width"=120)
```


<br><br>*... creating a text object ...*
```{r}
# initialize (with text or file)
quote <- 
  rtext$new(
    text = "Outside of a dog, a book is man's best friend. Inside of a dog it's too dark to read."
  )
```

<br><br>*... setting and getting data ...*
```{r}
# add some data
quote$char_data_set("first", 1, TRUE)
quote$char_data_set("last", quote$char_length(), TRUE)

# get the data
quote$char_data_get()
```


<br><br>*... text transformation and data update ...*
```{r}
# transform text
quote$char_add("[this is an insertion] \n", 47)

# get the data again (see, the data moved along with the text)
quote$text_get()
quote$char_data_get()
```


<br><br>*... using regular expression for setting data ...*
```{r}
# do some convenience coding (via regular expressions)
quote$char_data_set_regex("dog_friend", "dog", "dog")
quote$char_data_set_regex("dog_friend", "friend", "friend")
quote$char_data_get()
```

<br><br>*... data aggregation via regex ...*
```{r}
quote$tokenize_data_regex(regex="(dog)|(friend)", non_token = TRUE, join = "full")
```

<br><br>*... data aggregation by words ...*
```{r}
quote$tokenize_data_words(non_token = TRUE, join="full")
```

<br><br>*... data aggregation by lines ...*
```{r}
quote$tokenize_data_lines()
```

   

    
    
    
    
    
    
    
    
    
    
