---
title: "The diffrprojects manual for the technical interested"
author: "Peter Meißner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The *The diffrprojects manual for the technical interested* is a technical documentation of functions and functionality within the *diffrprojects* package. It is not tailored to the needs of the technical uninterested user but for developers and those who might dig deeper into how the package works, can be improved, or hacked. 



# Preparations

```{r}
library(diffrprojects)
```


# rtext

`rtext` is the diffrprojects text representation.

```{r}
robinson_crusoe_file <- dp_tf("robinson_crusoe_gutenberg.txt")
robinson_crusoe_text <- text_read(robinson_crusoe_file)
```

A rtext instance can be filled either by using a character vector:

```{r}
robinson_crusoe <- rtext$new(robinson_crusoe_text)
robinson_crusoe$text_show()
robinson_crusoe$info()
```

... or a file from which to read in the text.

```{r}
robinson_crusoe <- rtext$new(text_file=robinson_crusoe_file)
robinson_crusoe$text_show()
robinson_crusoe$info()
```





# test and dev tools

In need of files for testing? dp_df() is your friend.

```{r}
dp_tf()
```

In need of an extended ls() function, dp_ls() will help. 

```{r}
dp_ls(robinson_crusoe)
```



# tools

## text snippet

```{r}

```

