---
title: "The diffrprojects manual for the technical interested"
author: "Peter Meißner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The *The diffrprojects manual for the technical interested* is a technical documentation of functions and functionality within the *diffrprojects* package. It is not tailored to the needs of the technical uninterested user but for developers and those who might dig deeper into how the package works, can be improved, or hacked. 



# Preparations

```{r}
library(diffrprojects)
```


# dp_text

`dp_text` is the diffrprojects text representation.

```{r}
text_digibib <- 
  system.file("testfiles/robinson_crusoe_digibib.txt", package="diffrprojects")

text_fullbooks <- 
  system.file("testfiles/robinson_crusoe_dfullbooks.txt", package="diffrprojects")

text_gutenberg <- 
  system.file("testfiles/robinson_crusoe_gutenberg.txt", package="diffrprojects")

rc_g <- dp_text$new(file=text_gutenberg)

rc_g$show_text()
```


# tools

## text sni

```{r}

```

